### 2015-03-07 slides/auburn/dpp-intro.tex
Working on slides.

\begin{frame}[t]
    \frametitle{Sampling divergence models---a novel approach}
    \begin{itemize}[<+->]
        \item The divergence models are ways of assigning our taxa to events
        \item A Dirichlet process prior (DPP) model is a ``natural'' fit
            \begin{itemize}[<+->]
                \item Common nonparametric Bayesian approach to assigning
                    variables to an unknown number of categories
            \end{itemize}
    \end{itemize}

    \begin{uncoverenv}<2->
    \begin{center}
        \includegraphics[height=0.4\textheight]{../images/peter-dirichlet.jpg}
    \end{center}
    \end{uncoverenv}
\end{frame}

>>>>

\begin{frame}[t]
    \frametitle{Sampling divergence models---a novel approach}
    \begin{itemize}[<+->]
        \item The divergence models are ways of assigning our taxa to events
        \item A Dirichlet process prior (DPP) model is convenient and flexible
            solution
            \begin{itemize}[<+->]
                \item Common Bayesian approach to assigning variables to an
                    unknown number of categories
                \item Controlled by ``concentration'' parameter: $\alpha$
            \end{itemize}
    \end{itemize}

    \begin{uncoverenv}<2->
    \begin{figure}
    \begin{center}
        \includegraphics[height=0.4\textheight]{../images/peter-dirichlet.jpg}
        \caption{Peter Dirichlet}
    \end{center}
    \end{figure}
    \end{uncoverenv}
\end{frame}

### 2015-03-07 slides/auburn/full-phylo.tex
Working on slides.

\begin{frame}[t]
    \frametitle{New methods for inferring community history}
    \vspace{-5mm}
    \begin{minipage}[t][0.1\textheight][c]{1\linewidth}
    \begin{itemize}
        \item<2-> Incorporate comparative models of community-scale
            co-diversification into a full-phylogenetic framework
    \end{itemize}
    \end{minipage}

@@

\begin{frame}
    \begin{columns}
        \column{0.4\textwidth}
        \begin{minipage}[c]{\columnwidth}
        \begin{adjustwidth}{-2.3em}{}
        \begin{onlyenv}<1-6>
        \begin{itemize}
            \item<2-> Current phylogenetic methods assume speciation and extinction
                occur independently of one another
            \item<3-> We know this assumption is frequently violated
            \item<4-> I will generalize a birth-death model to accommodate
                ``shared'' events
            \item<6> Infer events jointly across multiple trees
        \end{itemize}
        \end{onlyenv}
        \begin{onlyenv}<7->
        \only<7->{\hspace{0.5cm}\textbf{\large Benefits:}\\}
        \begin{itemize}
            \item<8-> Improve phylogenetic inference and divergence-time estimation
            \item<9-> Provide a general framework for inferring the evolutionary
                history of whole communities
            \item<10-> Possible epidemiological applications
        \end{itemize}
        \end{onlyenv}
        \end{adjustwidth}
        \end{minipage}

        \column{0.6\textwidth}
        \begin{minipage}[t][\textheight][c]{\linewidth}
        \centerline{
        \includegraphics<1-3>[width=\columnwidth]{../images/bd-cartoon-no-lines.pdf}
        \includegraphics<4>[width=\columnwidth]{../images/bd-cartoon-shared.pdf}
        \includegraphics<5>[width=0.75\columnwidth]{../images/bd-cartoon-shared-space.pdf}
        \includegraphics<6->[width=0.75\columnwidth]{../images/bd-cartoon-2-trees-shared.pdf}
        }
        \end{minipage}
    \end{columns}
\end{frame}

>>>>

\begin{frame}[t]
    \frametitle{Next step: A general framework}
    \vspace{-5mm}
    \begin{minipage}[t][0.1\textheight][c]{1\linewidth}
    \begin{itemize}
        \item<2-> Incorporate comparative models of community-scale
            co-diversification into a full-phylogenetic framework
    \end{itemize}
    \end{minipage}

@@

\begin{frame}
    \frametitle{Next step: A general framework}

    \vspace{-5mm}
    \begin{columns}
        \column{0.4\textwidth}
        \begin{minipage}[c]{\columnwidth}
        \begin{adjustwidth}{-2.3em}{}
        \begin{onlyenv}<1-4>
        \begin{itemize}
            \item<1-> Relax the assumption of independence of events across the
                tree
            \item<2-> I will generalize a birth-death model to accommodate
                shared events
            \item<4-> Jointly infer co-diversification across multiple trees
        \end{itemize}
        \end{onlyenv}
        \begin{onlyenv}<5->
        \only<5->{\hspace{0.5cm}\textbf{\large Benefits:}\\}
        \begin{itemize}
            \item<6-> Improve phylogenetic inference and divergence-time estimation
            \item<7-> Provide a general framework for inferring shared
                evolutionary history across communities of species
            \item<8-> Epidemiological applications
        \end{itemize}
        \end{onlyenv}
        \end{adjustwidth}
        \end{minipage}

        \column{0.6\textwidth}
        \begin{minipage}[t][\textheight][c]{\linewidth}
        \centerline{
        \includegraphics<1>[width=\columnwidth]{../images/bd-cartoon-no-lines.pdf}
        \includegraphics<2>[width=\columnwidth]{../images/bd-cartoon-shared.pdf}
        \includegraphics<3>[width=0.7\columnwidth]{../images/bd-cartoon-shared-space.pdf}
        \includegraphics<4->[width=0.7\columnwidth]{../images/bd-cartoon-2-trees-shared.pdf}
        }
        \end{minipage}
    \end{columns}
\end{frame}

### 2015-03-07 slides/auburn/future-empirical.tex
Working on slides.

\begin{frame}
    \frametitle{Future directions: Gobi Desert}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{/home/jamie/Dropbox/field-photos/gobi/mongolia-auto-shop.jpg}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Future directions: Gobi Desert}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{/home/jamie/Dropbox/field-photos/gobi/mongolia-teratoscincus-przewalskii-landscape.jpg}
    \end{columns}
\end{frame}

\begin{frame}[t]
    \frametitle{Future directions: West-Central Africa}
    \begin{center}
        \includegraphics<1->[height={3cm}]{/home/jamie/Dropbox/field-photos/africa/Figure2_WAmapForestDist.png}
        \hspace{0.3mm}
        \includegraphics<1->[height={3cm}]{/home/jamie/Dropbox/field-photos/africa/Figure4_herps.jpeg}
    \end{center}

    \only<1>{
    \begin{center}
        \includegraphics[height={3.5cm}]{/home/jamie/Dropbox/field-photos/people/adam.png}
        \hspace{0.3mm}
        \includegraphics[height={3.5cm}]{/home/jamie/Dropbox/field-photos/people/fujita.jpg}
    \end{center}
    }

    \uncover<2->{
    \begin{center}
        \includegraphics[height=4.5cm]{../images/number-of-divs-africa.pdf}
    \end{center}
    }
\end{frame}

\begin{frame}
    \frametitle{``Micro''-islands of the Sunda Shelf}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{/home/jamie/Dropbox/field-photos/malaysia/malaysia-burungs.jpg}
    \end{columns}
\end{frame}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-present.png}}
\begin{frame}
    \frametitle{``Micro''-islands of the Sunda Shelf}
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
\begin{frame}
    \frametitle{``Micro''-islands of the Sunda Shelf}
\end{frame}
}

>>>>

% \begin{frame}
%     \frametitle{Empirical applications: Gobi Desert}
%     \vspace{-2mm}
%     \begin{columns}
%         % \column{\dimexpr\paperwidth-10pt}
%         \column{\dimexpr\paperwidth}
%         \includegraphics[width=\textwidth]{/home/jamie/Dropbox/field-photos/gobi/mongolia-auto-shop.jpg}
%     \end{columns}
% \end{frame}

% \begin{frame}
%     \frametitle{Empirical applications: Gobi Desert}
%     \vspace{-2mm}
%     \begin{columns}
%         % \column{\dimexpr\paperwidth-10pt}
%         \column{\dimexpr\paperwidth}
%         \includegraphics[width=\textwidth]{/home/jamie/Dropbox/field-photos/gobi/mongolia-teratoscincus-przewalskii-landscape.jpg}
%     \end{columns}
% \end{frame}

\begin{frame}
    \frametitle{Empirical applications: West-Central Africa}
    \begin{columns}
        \column{0.5\linewidth}
        % \begin{minipage}[c][\textheight][c]{\columnwidth}
        \begin{itemize}
            \item Did climate cycles drive diversification and community
                assembly across rainforest taxa?
            \item<2-> Funded by NSF
            \item<3-> Preliminary results with 300 loci from 3 taxa
        \end{itemize}

        \begin{minipage}[c][0.45\textheight][c]{\columnwidth}
        \begin{center}
            \only<1-2>{
            \includegraphics[height={2.5cm}]{/home/jamie/Dropbox/field-photos/people/adam.png}
            \hspace{0.3mm}
            \includegraphics[height={2.5cm}]{/home/jamie/Dropbox/field-photos/people/fujita.jpg}
            }

            \includegraphics<3->[width=0.9\columnwidth]{../images/number-of-divs-africa.pdf}
        \end{center}
        \end{minipage}

        \column{0.5\linewidth}
        % \begin{minipage}[c][\textheight][c]{\columnwidth}
        {\centering
            \includegraphics[width=\columnwidth]{/home/jamie/Dropbox/field-photos/africa/Figure2_WAmapForestDist.png}

            \vspace{5mm}

            \includegraphics[width=\columnwidth]{/home/jamie/Dropbox/field-photos/africa/Figure4_herps.jpeg}

        }
        % \end{minipage}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Empirical applications: Gobi Desert}
    \begin{columns}
        \column{0.5\linewidth}
        % \begin{minipage}[c][\textheight][c]{\columnwidth}
        \begin{itemize}
            \item Did the formation of the Gobi cause co-diversification
                across rock and sand-adapted communities of lizards?
            \item<2-> Funding from National Geographic Society to
                survey lizard biodiversity and collect preliminary
                genetic data
        \end{itemize}

        \column{0.5\linewidth}
        % \begin{minipage}[c][\textheight][c]{\columnwidth}
        {\centering
            \includegraphics[width=\columnwidth]{/home/jamie/Dropbox/field-photos/gobi/mongolia-auto-shop.jpg}

            \vspace{2mm}
            \includegraphics[width=\columnwidth]{/home/jamie/Dropbox/field-photos/gobi/mongolia-teratoscincus-przewalskii-landscape.jpg}
        }
        % \end{minipage}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Empirical applications: Southeast Asia}
    \begin{columns}
        \column{0.5\linewidth}
        \begin{itemize}[<+->]
            \item Did glacial cycles promote co-diversification across SE Asia?
            \item Compare patterns of diversification between mainland and
                continental and oceanic island systems
            \item Islands of the Sunda Shelf are an exciting system for
                comparative evolutionary biology
            \item NSF pre-proposal pending
        \end{itemize}

        \column{0.5\linewidth}
        {\centering
            {\setlength{\fboxsep}{0pt}
            \fbox{
                \hspace{-1.2mm}\includegraphics[width=\columnwidth]{../images/maps/se-asia-120-crop.png}
            }}
        }
    \end{columns}
\end{frame}
